---
output: github_document
---

# prepare-locs

A `targets` workflow for processing animal relocation data from the WEEL. 

```{r, eval = FALSE}
targets::tar_visnetwork()
```

```{r viz, echo = FALSE}
visNetwork::visNodes(targets::tar_visnetwork(), size = 20, font=list(size=25))
```

## Processed data


## Output: flag counts

## Output: column names

| Column name | Description | 
| ----------- | ----------- | 
| id          | unique animal identifier | 
| datetime    | date time in UTC | 
| x_long      | longitude, EPSG code provided in `metadata()`. see `R/metadata.R` | 
| y_lat       | latitude, EPSG code provided in `metadata()`. see `R/metadata.R` |
| flag        | comma separated flags indicating why locs are dropped and set to NaN | 
| doy         | date of year, integer. see `data.table::yday()` | 
| yr          | year, integer. see `data.table::year()` | 
| mnth        | month, integer. see `data.table::month()` | 
| x_proj      | projected x coordinate, output EPSG code in `metadata()`. see `R/metadata.R` |  
| y_proj      | projected y coordinate, output EPSG code in `metadata()`. see `R/metadata.R` |  
| epsg_proj   | output EPSG of 'x_proj' and 'y_proj' as set in `metadata()`. |
| [extracols] | eg. HERD. as provided in the `metadata()`.  see `R/metadata.R` |


## TODO

* 6030 not recognized by PROJ because it's not a complete CRS.. 


## Etc
Screening GPS fixes:

* https://ropensci.github.io/CoordinateCleaner/articles/Comparison_other_software.html
	+ missing coordinates
	+ lat == 0
	+ long == 0
	+ lat == long
	+ ...

* *Effects of habitat on GPS collar performance: using data screening to reduce location error*. Lewis et al. 2007
	+ drop 2D fixes
	+ threshold PDOP
	
* *Screening GPS telemetry data for locations having unacceptable error*. Laver et al. 





